Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-21 ms.tex
more clean-up, still focused on figure captions

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Planck SED for a single $N_{side}$=2048 pixel in the 
Polaris region. Note that the two lowest-frequency data points (\PLANCK~100, 
143 GHz) were not used in our fit, while the three lowest-frequency data
points were not used in the \cite{planckdust} fit.}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{Gridded posterior PDFs for three $N_{side}$=2048 pixels. Light green
crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
based on our MCMC sampling of the posteriors. The posterior distributions are 
in general extremely well-behaved, showing no multimodality or other 
pathological qualities. Our MCMC parameter and uncertainty estimates are in 
good agreement with the gridded posteriors. The colorscale is linear in 
$log(P)$, with black representing the maximum of $log(P)$ and white 
representing $max(log(P))-5$. Left: Low S/N pixel at high latitude in the 
Galactic north. Center: High S/N pixel in the Polaris region. Right: Low S/N 
pixel at high latitude in the Galactic south.}
\end{center}
\end{figure*}

@@

With values for $\rho_{CIBA, \nu_i, \nu_j}$ from \cite{covarciba}. The approach
we have taken in accounting for the CIBA is similar to that of 
\cite{planckdust}, Appendix B, in that we treat the CIBA amplitude in each 
pixel as a Gaussian random draw. However, instead of performing a separate 
analysis to gauge the uncertainty on derived dust parameters due to the CIBA, 
we allow the CIBA covariance to propagate naturally into our uncertainties via 
the likelihood function. Still, our treatment of the CIBA is a major 
oversimplification relative to the ideal situation in which the detailed 
spatial structure of the CIBA would be thoroughly accounted for or even removed
by subtraction.

@@

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of SFD temperature, two-component 
model $T_2$, and \cite{planckdust} temperature (labeled $T_{R1.20}$) for a
 $10.5^{\circ}\times8.3^{\circ}$  region centered about 
$(l,b) = (111.6^{\circ}, 18.3^{\circ})$. Note the differing colorscales. Both 
models incorporating \PLANCK~data clearly show a major improvement in angular 
resolution relative to SFD.}
\end{center}
\end{figure}

@@

Lastly, during post burn-in sampling, we also estimate the monochromatic 
two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and the 
545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
$M_{545}$ are more readily useful than the sampling parameters themselves for 
translating our fit results into predictions of reddening ($\S$\ref{sec:ebv}) 
and thermal dust emission ($\S$\ref{sec:lofreq}), respectively. At high
Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and
typical $\tilde{I}_{545}$ fractional uncertainty of 13\%.

@@

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
$\chi^2_{\nu}$=$\langle \chi^2_{p, \nu} \rangle$ for various dust SED models. 
For single-MBB models with spatially constant $\beta$, we varied $\beta$ 
between 1 and 2 (x axis), achieving reduced chi-squared $\chi^2_{\nu}$ shown by
the black line, with $\beta$=1.57 providing the best fit. Horizontal lines 
indicate $\chi^2_{\nu}$ for other dust SED models considered, including the 
FDS99 best-fit model and our best-fit \PLANCK+DIRBE model from 
$\S$\ref{sec:global}. The minimum $\chi^2_{\nu}$ was achieved with
two-componenent `model 2' from Table \ref{tab:global} (horizontal magenta 
line).}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid.eps, width=6.6in}
\caption{\label{fig:resid} (top left) Residuals of $E(B-V)_{2comp}$ relative to
$E(B-V)_{SSPP}$ as a function of $E(B-V)_{SFD}$. The grayscale represents the 
conditional probability within each $E(B-V)_{SFD}$ bin. The central black line 
shows the moving median. The upper and lower black lines represent the moving 
75th and 25th percentiles respectively. (bottom left) Residuals of 
$E(B-V)_{2comp}$ relative to $E(B-V)_{SSPP}$ as a function of hot dust 
temperature $T_2$. (top right) Same as top left, but illustrating the residuals
of $E(B-V)_{mbb}$, our calibration of the \cite{planckdust} $\tau_{353}$ to 
$E(B-V)_{SSPP}$. (bottom right)  Same as bottom left, but showing the 
$E(B-V)_{mbb}$ residuals as a function of the single-MBB dust temperature from 
\cite{planckdust}. The temperature axes always range from the 
0.4$^{th}$ percentile to 99.6$^{th}$ percentile temperature values.}
\end{center}
\end{figure*}

@@

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{\label{fig:results} (top) Hot dust temperature derived from our 
full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD 
\texttt{i100}, downbinned to 27.5$'$ resolution. (bottom) Corresponding
full-sky map of best-fit 545 GHz optical depth.}
\end{center}
\end{figure*}

>>>>

\begin{figure}
\begin{center}
\epsfig{file=sed.eps, width=3.3in}
\caption{\label{fig:sed} Observed SED (black points and error bars) and 
best-fit thermal dust emission models for a single $N_{side}$=2048 pixel in the
Polaris flare region. The best-fit two-component model (black line) is derived 
based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ resolution. Note 
that the two lowest-frequency data points were not used in the two-component 
fit shown, while the three lowest-frequency data points were not used in the 
\cite{planckdust} single-MBB fit shown (cyan).}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=posteriors.eps, width=7.0in}
\caption{\label{fig:post} Gridded posterior PDFs for three $N_{side}$=2048 
pixels, based on \PLANCK~217-857 GHz and SFD 100$\mu$m at full $6.1'$ 
resolution. The colorscale is linear in $log(P)$, with black corresponding to 
the maximum of $log(P)$ and white representing $max[log(P)]-5$. Light green 
crosses and ellipses mark the best-fit parameters and $1\sigma$ uncertainties 
based on our MCMC sampling of the posteriors. Our MCMC parameter and 
uncertainty estimates are in good agreement with those based on gridded 
posteriors. These three pixels are also representative in that we find the 
posterior distributions from Equation \ref{eqn:post} are in general extremely 
well-behaved, showing no multimodality or other pathological qualities. Left: 
Low S/N pixel at high latitude in the Galactic north. Center: High S/N pixel in
the Polaris flare region. Right: Low S/N pixel at high latitude in the Galactic
south.}
\end{center}
\end{figure*}

@@

With values for $\rho_{CIBA, \nu_i, \nu_j}$ from \cite{covarciba}. The approach
we have taken in accounting for the CIBA is similar to that of 
\cite{planckdust}, Appendix B, in that we treat the CIBA amplitude in each 
pixel as a Gaussian random draw. However, instead of performing a separate 
analysis to gauge the uncertainty on derived dust parameters due to the CIBA, 
we allow the CIBA covariance to propagate naturally into our uncertainties via 
the likelihood function. Still, our treatment of the CIBA is a major 
oversimplification; a more sophisticated approach that accounts for the 
detailed CIBA spatial structure, or even removes the CIBA by subtraction would
be preferable.

@@

\begin{figure}
\begin{center}
\epsfig{file=tcomparison.eps, width=3.3in}
\caption{\label{fig:comparison} Comparison of temperature maps based on FIR 
dust emission over a $10.5^{\circ}\times8.3^{\circ}$ region centered about 
$(l,b) = (111.6^{\circ}, 18.3^{\circ})$. Top: SFD temperature map based on 
DIRBE $100\mu$m and $240\mu$m, with $\sim$1.3$^{\circ}$ resolution. Center: 
$6.1'$ resolution two-component temperature based on \PLANCK~217-857 GHz and 
SFD 100$\mu$m. Bottom: \cite{planckdust} single-MBB temperature map based on 
\PLANCK~353-857 GHz and 100$\mu$m data, with $5.1'$ FWHM. Both temperature maps
incorporating \PLANCK~observations clearly show a major improvement in angular 
resolution relative to SFD.}
\end{center}
\end{figure}

@@

Lastly, during post burn-in sampling, we also estimate the monochromatic 
two-component intensity at 545 GHz, $M_{545}$ = $\langle M_{545, j} \rangle$ = 
$\langle \tilde{I}_{545, j}/b_{545}(T_{2,j}) \rangle$, its variance, and the 
545 GHz optical depth $\tau_{545}$=$\langle \tau_{545, j} \rangle$ = 
$\langle M_{545, j}/S_{545, j} \rangle$ and its variance. $\tau_{545}$ and 
$M_{545}$ are more readily useful than the sampling parameters themselves for 
translating our fit results into predictions of reddening ($\S$\ref{sec:ebv}) 
and thermal dust emission ($\S$\ref{sec:lofreq}), respectively. At high
Galactic latitude, we find a typical $T_2$ uncertainty of 0.45 K, and
typical $\tilde{I}_{545}$ fractional uncertainty of 13\%. Figure \ref{fig:sed}
shows a summary of the observed SED and resulting best-fit two-component
model for a single $N_{side}$=2048 pixel, and Figure \ref{fig:post} 
shows posterior PDFs for three pixels.

@@

\begin{figure}
\begin{center}
\epsfig{file=chi2_dirbe.eps, width=3.3in}
\caption{\label{fig:chi2_dirbe} Comparison of goodness-of-fit, 
$\chi^2_{\nu}$=$\langle \chi^2_{p, \nu} \rangle$, for various dust SED models,
as described in $\S$\ref{sec:hier}. For single-MBB models with spatially 
constant $\beta$, we varied $\beta$ between 1 and 2 (horizontal axis), 
achieving reduced chi-squared $\chi^2_{\nu}$ shown by the black line, with 
$\beta$=1.57 providing the best fit. Horizontal lines indicate $\chi^2_{\nu}$ 
for other dust emission models considered, including the FDS99 best-fit 
two-component model (Table \ref{tab:global}, model 1, red) and the 
\cite{planckdust} single-MBB model (green). The minimum $\chi^2_{\nu}$ is 
achieved with two-componenent `model 2' from Table \ref{tab:global} (magenta).}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid.eps, width=6.6in}
\caption{\label{fig:resid} (top left) Residuals of $E(B-V)_{2comp}$ relative to
$E(B-V)_{SSPP}$ as a function of $E(B-V)_{SFD}$. The grayscale represents the 
conditional probability within each $E(B-V)_{SFD}$ bin. The central black line 
shows the moving median. The upper and lower black lines represent the moving 
75th and 25th percentiles respectively. (bottom left) Residuals of 
$E(B-V)_{2comp}$ relative to $E(B-V)_{SSPP}$ as a function of hot dust 
temperature $T_2$. (top right) Same as top left, but illustrating the residuals
of $E(B-V)_{mbb}$, our calibration of the \cite{planckdust} $\tau_{353}$ to 
$E(B-V)_{SSPP}$. (bottom right)  Same as bottom left, but showing the 
$E(B-V)_{mbb}$ residuals as a function of the single-MBB dust temperature from 
\cite{planckdust}. The temperature axes always range from the 0.4$^{th}$ 
percentile temperature value to the 99.6$^{th}$ percentile temperature value.}
\end{center}
\end{figure*}

@@

\begin{figure*} [ht]
\begin{center}
\epsfig{file=results.eps, width=7.0in}
\caption{\label{fig:results} (top) Hot dust temperature derived from our 
full-resolution two-component model fits of \PLANCK~217-857 GHz and SFD 
100$\mu$m, downbinned to 27.5$'$ resolution. (bottom) Corresponding full-sky 
map of best-fit 545 GHz optical depth.}
\end{center}
\end{figure*}
